Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
revise intro para of sec 4

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

>>>>

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:correctness}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely\;\text{\lazyD} $ cast 
representation respects the semantics of \lazyD\ cast calculus. Having this 
theorem means when people want to prove a \lazyD\ cast reprentation is correct, 
all they have to do is to prove that their cast representation is $ surely \;
LazyD $ and apply our framework to this proof, which should be much simpler 
than proving equivalence of semantics.
We are working on a similar theorem for \lazyUD{}.
